Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-03-31 Manuscript/Figures/figure_legends.Rmd

**Figure 5. Predicted TAD boundaries are enriched with known molecular drivers of the 3D chromatin architecture.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878). The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox. Called TADs are outlined in blue. The blue vertical lines represent a called TAD boundary identified by the ARROWHEAD algorithm. The black line represents the predicted probability of each base pair being a TAD boundary. Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis. The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning. <!--(B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.-->

>>>>

**Figure 5. Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878). The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.The blue vertical lines represent called boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above. The black line represents the predicted probability of each base pair being a TAD boundary when validated by *TADRF*. Collections of red vertical lines represent base pairs whose predictive probability exceed the ROC threshold, labeled as *predicted TAD boundary areas* (PTBA). The midpoints of spatially similar PTBA were clustered together into *predicted TAD boundary regions* (PTBR), denoted by the yellow regions along the x-axis. The green vertical lines represent the *predicted TAD boundary points* (PTBA) identified by *preciseTAD*, with the corresponding predicted TADs outlined above in green. <!--(B) Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by SMC3, ZNF143, CTCF, and RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.-->

### 2020-03-31 Manuscript/manuscript.Rmd

![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878). The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.  Called TADs are outlined in blue.  The blue vertical lines represent a called TAD boundary identified by the ARROWHEAD algorithm. The black line represents the predicted probability of each base pair being a TAD boundary. Regions of adjacent base pairs with probability of 1 are represented by the green regions along the x-axis. The green vertical lines represent the subsequent base pair predicted to be a TAD boundary using medoid partitioning.](Figures/visualizing_ptbp_and_ctbp.png)

>>>>

![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** (A) Visualizing locations of predicted and called TAD boundaries (chr 22: 17389000-18011000; GM12878). The upper triangular contact map shows the normalized number of contacts within the specified window using the JUICER toolbox.The blue vertical lines represent called boundaries identified by ARROWHEAD, with the corresponding called TADs outlined in blue on the upper diagonal contact matrix above. The black line represents the predicted probability of each base pair being a TAD boundary when validated by *TADRF*. Collections of red vertical lines represent base pairs whose predictive probability exceed the ROC threshold, labeled as *predicted TAD boundary areas* (PTBA). The midpoints of spatially similar PTBA were clustered together into *predicted TAD boundary regions* (PTBR), denoted by the yellow regions along the x-axis. The green vertical lines represent the *predicted TAD boundary points* (PTBA) identified by *preciseTAD*, with the corresponding predicted TADs outlined above in green.](Figures/visualizing_ptbp_and_ctbp.png)
